Multi-level modeling with Openflexo/\FML

### 2021-09-20 7-requirementssatisfaction.tex

    \item \emph{Ontological instantiation} (\textit{O.Inst.}): fulfillment of a requirement is obtained by the relation between an instance and its type definition instance (for example for \textbf{S3} : \textit{developer} has the dual concept nature in \textit{Acme metamodel} and instance nature in \textit{Acme model}).

>>>>

    \item \emph{Ontological instantiation} (\textit{O.Inst.}): fulfillment of a requirement is obtained by the relation between an instance and its type definition instance (for example \todo[inline]{the notion of \textit{developer} of \textbf{S3} is implemented by both a concept in \textit{Acme metamodel} and an instance in \textit{Acme model}).}

### 2021-09-20 9-relatedworks.tex

More similar to us, \cite{deeptelos2019} use DeepTelos \parencite{deeptelos2016}, an extension of the Telos language \parencite{telos1990} in order to solve the process challenge. As with Openflexo and \FML, they do not use explicit (numbered) levels nor potency. However, unlike Openflexo, DeepTelos integrates a multi-level modeling specific construct similar to the PowerType \parencite{atkinson2001essence} pattern they call \emph{most general instances}.

>>>>

More similar to us, in the submission \parencite{deeptelos2019}, the author uses DeepTelos \parencite{deeptelos2016}, an extension of the Telos language \parencite{telos1990} in order to solve the process challenge. As with Openflexo and \FML, they do not use explicit (numbered) levels nor potency. However, unlike Openflexo, DeepTelos integrates a multi-level modeling specific construct similar to the PowerType \parencite{atkinson2001essence} pattern they call \emph{most general instances}.
